Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-07-28 paper-v1.tex
Figure caption. @naszam

\begin{figure}
\centering
\includegraphics[scale=0.28]{AntsReview}
\caption{\textbf{a} The core contract of the protocol, it implements a bounty system with the functions listed.
\textbf{b} The module inherited by AntsReview, that manages the access control of the protocol, adding and removing issuers and peer-reviewers.
\textbf{c} The native token used in the protocol that inherits the \textbf{d} contract from OpenZeppelin. It's linked to \textbf{a} and to \textbf{e}, to be wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
\textbf{f} Represents the integration with IPFS to upload the paper, requirements and peer-reviews and store the hash as \emph{proof of existence} into AntsReview.
\textbf{g} Represents the integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
\textbf{h} The library used by the protocol for secure contract development, with the modules listed.}
\label{fig:contracts}
\end{figure}

@@

\subsubsection{AntsReview.}
AntsReview (see Figure \ref{fig:contracts}a) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}. AntsReview implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
\newline In order to create a transparent and openly accessible AntReview, Alice has to complete a series of required tasks:
 \newline 1. \emph{upload of the file} containing the requirements of the peer-review and the paper to be reviewed into IPFS and specification of the IPFS hash to be stored in the Ethereum blockchain as PoE;
 \newline 2. \emph{specification of a deadline} in the form of a unix timestamp after which the fulfillment will no longer be accepted;
 \newline 3. \emph{specification of the amount of Ether} for the reward that will be transferred from Alice to the contract.
 \newline Bob (peer-reviewer) downloads the file with Alice's paper and requirements by leveraging on the content-addressing feature of IPFS, that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer-review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by specifying the AntReview of interest as well as the IPFS Hash of the peer-review uploaded on IPFS.
Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the AntReview as well as the peer-review of interest, that will transfer the reward specified for the AntReview from the contract to Bob.
If Alice doen't receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, by specifying the AntReview of interest, and the contract will transfer the reward for the AntReview back to Alice.

@@

\subsubsection{Supplementary material}
Source Code, DOI: 10.5281/ZENODO.3829162
\newline Demo (PoC), DOI: 10.5281/ZENODO.3829183

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.28]{AntsReview}
\caption{Exagones represent the protocol's smart contracts. Ellipse represents the smart contract inherited by AntsReview. Clouds represent integrations into the protocol. Rectangles represent smart contracts' libraries.
\textbf{a)} Core contract of the protocol implementing a bounty system with the functions listed.
\textbf{b)} Module inherited by AntsReview: it manages the access control of the protocol by adding and removing issuers and peer-reviewers.
\textbf{c)} Native token used in the protocol that inherits the \textbf{d)} contract from \emph{OpenZeppelin}. It is linked to \textbf{a)} and to \textbf{e)}, wrapped into \emph{zkANTS} to implement private \emph{ANTS} transactions on Ethereum.
\textbf{f)} Integration with IPFS to upload papers, requirements and peer-reviews and store the hash as \emph{PoE} into AntsReview.
\textbf{g)} Integration with De-Fi services like \emph{Dai} and \emph{Chai}, to be used as tokens in the protocol.
\textbf{h)} Library used by the protocol for secure contract development with the modules listed.}
\label{fig:contracts}
\end{figure}

@@

\subsubsection{AntsReview.}
AntsReview (see Figure \ref{fig:contracts}a) is the core of the smart contracts written in \emph{Solidity}\footnote[6]{\emph{Solidity}.\textsc{URL:}https://solidity.readthedocs.io.}, an object-oriented programming language for writing smart contracts that runs on the Ethereum Virtual Machine, deployed on Ethereum Rinkeby's Testnet\footnote[7]{\emph{Rinkeby Testnet}.\textsc{URL:}https://rinkeby.etherscan.io.}. AntsReview implements a bounty-like system where Alice (issuer) can issue an AntReview with the function \emph{issueAntReview()}.
\newline In order to create a transparent and openly accessible AntReview, Alice has to complete a series of required tasks:
 \newline 1. \emph{upload of the file} containing the requirements of the peer-review and the paper to be reviewed into IPFS and specification of the IPFS hash to be stored in the Ethereum blockchain as PoE;
 \newline 2. \emph{specification of a deadline} in the form of a unix timestamp after which the fulfillment will no longer be accepted;
 \newline 3. \emph{specification of the amount of Ether} for the reward that will be transferred from Alice to the contract.
 \newline Bob (peer-reviewer) downloads the file with Alice's paper and requirements by leveraging on the content-addressing feature of IPFS, that allows anyone to find the document using an IPFS explorer; subsequently, Bob can submit a peer-review before the deadline by fulfilling the AntReview created by Alice, with the function \emph{fulfillAntReview()}, by specifying the AntReview of interest as well as the IPFS Hash of the peer-review uploaded on IPFS.
Alice can accept the peer-review submitted by Bob with the function \emph{acceptAntReview()}, by specifying the AntReview as well as the peer-review of interest, that will transfer the reward specified for the AntReview from the contract to Bob.
If Alice does not receive any peer-review, she can cancel the AntReview with the function \emph{cancelAntReview()}, by specifying the AntReview of interest, and the contract will transfer the reward for the AntReview back to Alice.

@@

\subsubsection{Supplementary material}
Source Code, DOI: 10.5281/zenodo.3953999
\newline Proof of Concept (PoC) DApp, \url{antsreview.on.fleek.co}
\newline Demo (PoC), DOI: 10.5281/zenodo.3964466
